\documentclass[a4paper]{tufte-handout}

\usepackage{dashrule}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{units}

\usepackage{draftwatermark}
\SetWatermarkText{Draft}
\SetWatermarkScale{1.5}

\title{Officer Duties Bye-Law}
% \author[The ICDS Committee]{The ICDS Committee}
\date{Proposed at the General Meeting on 03/11/15}

\newcommand{\policyOffset}{12pt}

\newcommand{\policyCspp}[2][\policyOffset]{\marginnote[#1]{\textsc{CSP Policy \S#2}}}
\newcommand{\policyCspEquip}[2][\policyOffset]{\marginnote[#1]{\textsc{CSP Equipment Policy \S#2}}}
\newcommand{\policyBye}[2][\policyOffset]{\marginnote[#1]{\textsc{Bye-laws \S#2}}}
\newcommand{\policyAE}[2][\policyOffset]{\marginnote[#1]{\textsc{A\&E Standing Orders \S#2}}}
\newcommand{\policyHs}[2][\policyOffset]{\marginnote[#1]{\textsc{Health \& Safety Policy \S#2}}}
\newcommand{\policyPub}[2][\policyOffset]{\marginnote[#1]{\textsc{Publicity Policy \S#2}}}
\newcommand{\policyTankard}[1][\policyOffset]{\marginnote[#1]{\textsc{Tankards Policy}}}

\addtolength{\hoffset}{24pt}

\begin{document}

\maketitle

\begin{fullwidth}
\itshape

\begin{abstract}
This bye-law assigns responsibilities to officers of the Committee.
\end{abstract}
\end{fullwidth}

\hdashrule{15cm}{1.1pt}{1.1pt}

\section{Introduction}
\begin{enumerate}
    \item This document shall inherit all provisions and definitions given in the Imperial College Dramatic Society Constitution (ICDS Constitution).
    \item This document shall be a bye-law of ICDS under the terms of the ICDS Constitution.
    \item If this document conflicts with the ICDS Constitution, the ICDS Constitution shall take precedence.
    \item The following responsibilities are to be taken in addition to those mandatory duties indicated in the ICDS Constitution.
\end{enumerate}

\subsection{Responsibilities of the Officers}
\begin{enumerate}[resume]
    \item \newthought{The President:}
        \begin{enumerate}
            \item shall represent the Society to other societies, the public, external bodies, and any body of the Union (such as the Arts and Entertainments Management Group).
            \item is ultimately responsible for the artistic output of the Society.
            \item shall liaise with COMUS to further alumnus integration.
            \item shall be responsible for ensuring that risks arising during the execution of the Society's activities are appropriately identified and mitigated.
            \item \policyHs{26.3.4} shall be responsible for informing the Union of any controls and provisions made to identify and mitigate risks to Society Members (to include the annual submission of a risk assessment).
            \item shall be responsible for ensuring that all plays produced by the Society have assigned to them a \textsc{Producer}, who shall be a Member of the Society responsible for the execution of the play (to include its financial aspects), and who shall be answerable to the Committee. This Producer must not also be the show's director, except in the case of simple plays if considered appropriate by the committee.
            \item the authority to authorise publicity may be revoked or further devolved as the President sees fit.
    \end{enumerate}
    \item \newthought{The Vice-President:}
        \begin{enumerate}
            \item shall assist the President in the running of the Society.
            \item \policyPub{4} may be delegated authority by the President to authorise publicity.
        \end{enumerate}
    \item \newthought{The Treasurer:}
        \begin{enumerate}
            \item shall carry out the day-to-day financial duties of the Society.
            \item shall be responsible for participating in the Union's annual budgeting process.
            \item shall ensure that an appropriately-qualified person (usually the Producer) keeps appropriate accounts for every show produced by the Society.
            \item shall inspect the budget for every show produced by the Society, and if they deem it to be acceptable, approve it.
        \end{enumerate}
    \item \newthought{The Honorary Secretary:}
        \begin{enumerate}
            \item \policyPub{4} may be delegated authority by the President to authorise publicity.
            \item shall be responsible for minuting all meetings of the Society and maintaining a public archive of such minutes.
            \item shall be responsible for keeping records of the running of the Society and maintaining its archives in good order.
            \item shall be responsible for communicating announcements to the membership of the Society and the Committee.
            \item shall be responsible for ensuring that all documentation required by the CSP Policy, \S83 are submitted as required.
        \end{enumerate}
    \item \newthought{The Acting Director:}
        \begin{enumerate}
            \item shall have responsibility for the training of Members of the Society in fields relating to acting, to include the organisation of acting workshops.
            \item shall be responsible for the Society's representation at drama festivals as directed by the Committee.
        \end{enumerate}
    \item \newthought{The Technical Director:}
        \begin{enumerate}
            \item shall be responsible for ensuring that a Production Manager is assigned to all events, who shall be answerable to the Committee for that event. The Production Manager, which is not necessarily an exclusive role, may be any member of the society, including the Technical Director. An external event is one to which the Society contributes but which the Society does not principally control or fund.
            \item shall be responsible for the maintenance of the DramSoc Storeroom.
            \item shall be responsible for liaising with the Union over the management, maintenance and upkeep of the Union Concert Hall.
            \item shall represent the Society to the Union, College, other societies, and any other clients for all relevant matters as described above.
            \item shall be responsible for the creation, regular review, and enforcement of a code of practice for technicians covering aspects of safety procedure and working practice, to which all Members of the Society must adhere.
            \item \policyCspEquip{A3, {\S}A5 \& {\S}B7} shall have overall responsibility for the Society's equipment, including its management and safe usage.
            \item \policyCspEquip{A5.2 \& {\S}A5.3} shall be responsible overall for the training of Members in all aspects of the Society's technical activities.
            \item \policyCspEquip{C} shall ensure that all equipment is maintained and kept securely in good safe working order, and that records are kept of this maintenance and of the equipment owned by the Society.
            \item \policyCspEquip{A7} shall ensure that all equipment and storage is appropriately labelled.
            \item \policyCspEquip{A6} shall ensure that appropriate records are kept and fees are lodged with the Treasurer when equipment is hired.
            \item shall be assisted in these aims and responsibilities by the Lighting Director, the Sound Director and the Set, Props and Costumes Director as described below.
        \end{enumerate}
    \item \newthought{The Lighting Director:}
        \begin{enumerate}
            \item shall have general responsibility for the Society's lighting equipment.
            \item shall be responsible for the maintenance of the Society's lighting equipment.
            \item shall be responsible for advising the Committee on the maintenance of an appropriate level of technical capability in the lighting department.
            \item shall be responsible for the training of other Members of the Society in fields relating to lighting design and engineering.
        \end{enumerate}
    \item \newthought{The Sound Director:}
        \begin{enumerate}
            \item shall have general responsibility for the Society's sound equipment.
            \item shall be responsible for the maintenance of the Society's sound equipment.
            \item shall be responsible for advising the Committee on the maintenance of an appropriate level of technical capability in the sound department.
            \item shall be responsible for the training of other Members of the Society in fields relating to sound design and engineering.
        \end{enumerate}
    \item \newthought{The Set, Props and Costumes Director:}
        \begin{enumerate}
            \item shall be responsible for the storage and upkeep of the Society's props, costumes, and items of set.
            \item shall be responsible for the upkeep of the Society's prop, costume, and set storage spaces.
            \item shall be responsible for the management and maintenance of all construction tools and instructing Members on their correct and safe use.
            \item shall provide support, guidance and assistance to set, prop and costume designers for the Society's shows.
            \item shall manage the hire of set, costumes and props to other Union bodies and to external parties.
        \end{enumerate}
    \item \newthought{The Pub. Officer:}
        \begin{enumerate}
            \item shall be responsible for ensuring that the Society and its activities are publicised to Members of the College.
            \item shall be responsible for the design of the Society's publicity materials.
            \item shall maintain a coherent and consistent brand image for the Society.
            \item shall ensure that publicity is orchestrated for the Society's plays.
            \item shall be responsible for maintaining the content of the Society's website.
            \item shall be responsible for managing the Society's social media accounts.
            \item shall be responsible for the production of Society merchandise.
            \item shall ensure that photographs are taken and archived of every Society show, along with that show's publicity material.
            \item \policyPub{4} may be delegated authority by the President to authorise publicity.
        \end{enumerate}
    \item \newthought{The Social Secretary:}
        \begin{enumerate}
            \item shall be responsible for the organisation of social events to promote the cohesion and happiness of the Members of the Society.
            \item shall provide mandatory fun.
        \end{enumerate}
    \item \newthought{The Systems Administrator:}
        \begin{enumerate}
            \item shall be responsible for the design, upkeep, security and maintenance of the computer systems and networks utilised in the day-to-day running of the Society, to include:
                \begin{enumerate}
                    \item Servers
                    \item Workstations
                    \item Routers and switches
                    \item E-Mail accounts
                    \item Mailing lists
                    \item Domains and DNS records
                    \item Printers
                    \item Other information systems as may from time to time become necessary, as directed by the Committee.
                \end{enumerate}
            \item shall assist the Pub. Officer in the maintenance of the website by providing them with the necessary tools to update it.
        \end{enumerate}
    \item \newthought{The Ordinary Committee Member:}
        \begin{enumerate}
            \item shall contribute to the running of the Society by assisting the Committee as appropriate.
        \end{enumerate}
\end{enumerate}

\end{document}

% vim: expandtab:ts=4:sw=4